\section{Analysis: Comparison of different SLAM approaches for a driverless race car (Le Large, Bieder, and Lauer, 2021)}\label{sec:le-large-bieder-lauer-2021}

\subsection{Bibliographic Information}\label{subsec:bibliographic-information2}
\begin{itemize}
    \item \textbf{Title:} Comparison of different SLAM approaches for a driverless race car
    \item \textbf{Authors:} Le Large, Bieder, and Lauer
    \item \textbf{Year:} 2021
    \item \textbf{Type:} Journal/Conference Paper (assumed, based on context)
\end{itemize}

\subsection{Abstract/Core Focus}\label{subsec:abstract/core-focus2}
This paper presents a comprehensive comparison of EKF SLAM, FastSLAM, and GraphSLAM for a driverless race car in Formula Student. It evaluates accuracy, computational efficiency, and robustness through simulation and real-world tests on a Formula Student platform. GraphSLAM is found to be most accurate, while EKF SLAM is more resource-efficient. The paper also discusses practical implementation challenges like sensor selection, data association, and dynamic environments.

\subsection{Methodology}\label{subsec:methodology}
\begin{itemize}
    \item Systematic comparison using a consistent testing framework (simulation and real-world tracks).
    \item Modular software architecture for substituting SLAM approaches with consistent sensor inputs (LiDAR, cameras, wheel encoders) and evaluation metrics.
    \item Sensor calibration and synchronisation emphasised.
    \item Performance measured against ground truth (high-precision GPS), evaluating map accuracy, localisation error, processing time, and memory across different track layouts/conditions.
\end{itemize}

\subsection{Key Findings}\label{subsec:key-findings}
\begin{itemize}
    \item GraphSLAM: Superior accuracy in mapping and localisation (approx. 30\% lower position error).
    \item EKF SLAM: Lowest computational requirements, suitable for resource-constrained systems.
    \item FastSLAM: Balanced accuracy/performance, but sensitive to parameter tuning.
    \item All approaches struggled with dynamic obstacles and reflective surfaces.
    \item Visual feature integration with LiDAR improved localisation in feature-sparse areas.
    \item Sensor fusion (short-range precision + long-range context) is critical for robustness.
\end{itemize}

\subsection{Strengths of the Research}\label{subsec:strengths-of-the-research2}
\begin{itemize}
    \item \textbf{Direct Comparison:} Offers a focused comparison of key SLAM algorithms relevant to autonomous racing.
    \item \textbf{Formula Student Context:} Directly applicable to the honours project domain, using a Formula Student platform and addressing relevant challenges.
    \item \textbf{Dual Evaluation:} Combines simulation and real-world testing for comprehensive validation.
    \item \textbf{Practical Insights:} Addresses real-world implementation issues (sensor fusion, data association).
    \item \textbf{Quantitative Metrics:} Provides clear performance metrics for different SLAM approaches.
\end{itemize}

\subsection{Weaknesses/Limitations of the Research}\label{subsec:weaknesses/limitations-of-the-research2}
\begin{itemize}
    \item \textbf{Software Version Dependency:} Findings tied to specific SLAM library versions and software states in 2021.
    \item \textbf{Hardware Specificity:} Results may be influenced by the specific sensor suite and computational hardware of the KA-RaceIng car.
    \item \textbf{Limited Scope of GAs:} The paper focuses on SLAM, not on the subsequent path planning or GA optimisation, which is the core of the honours project.
\end{itemize}

\subsection{Relevance to Honours Project: "Investigating the use of Genetic Algorithms to optimise a path planning algorithm within the Context of a Formula Student Team"}\label{subsec:relevance-to-honours-project:-"investigating-the-use-of-genetic-algorithms-to-optimise-a-path-planning-algorithm-within-the-context-of-a-formula-student-team"3}

\subsubsection{Input Relevance}
\begin{itemize}
    \item \textbf{SLAM Algorithm Selection:} Provides critical data for selecting or developing a SLAM algorithm that will produce the map input for the GA path planner.
    The choice of SLAM (e.g., GraphSLAM for accuracy vs EKF for efficiency) directly impacts the quality and characteristics of the map data the GA will use.
    \item \textbf{Map Characteristics Understanding:} The paper details the expected accuracy, consistency, and potential failure modes of maps generated by different SLAM approaches in a Formula Student context.
    This informs the GA design regarding how to handle map imperfections or uncertainties.
    \item \textbf{Sensor Data Insights:} Discussion on sensor fusion and data association helps in understanding the raw inputs to the SLAM system, which indirectly affects the final map quality for the GA.
\end{itemize}

\subsubsection{Process Relevance}
\begin{itemize}
    \item \textbf{Informing SLAM Component of Project:} If the honours project involves implementing or choosing a SLAM system, this paper is a primary reference for making informed decisions based on performance trade-offs.
    \item \textbf{Understanding SLAM Output for GA:} The GA path planner must be designed to work with the specific type of map output by the chosen SLAM system (e.g., point clouds, feature lists, occupancy grids). This paper helps anticipate what that output will look like.
    \item \textbf{Simulation Environment Design:} The methodologies for testing SLAM in simulation (and real-world) can inform how the simulation environment for the GA path planner should be designed, particularly in how it models sensor data and track features relevant to SLAM.
    \item \textbf{Benchmarking SLAM Performance:} While the project focuses on GA path planning, the performance of the underlying SLAM system is crucial. This paper provides benchmarks for what constitutes good SLAM performance in this context.
\end{itemize}

\subsubsection{Output Relevance}
\begin{itemize}
    \item \textbf{Quality of Input to GA:} The success of the GA-optimised path planner heavily depends on the quality of the SLAM-generated map. This paper helps set expectations for that map quality and how it might affect the final path planning performance.
    \item \textbf{System Integration Context:} The paper underscores that SLAM is part of a larger autonomous system. The GA path planner is another component, and understanding SLAM helps in designing the interface between these components.
    \item \textbf{Justification for SLAM Choice (if applicable):} If a specific SLAM approach is chosen as part of the project, this paper provides strong justification for that choice based on empirical evidence in a relevant context.
\end{itemize}

\subsection{Further Notes/Actionable Insights}\label{subsec:further-notes/actionable-insights3}
\begin{itemize}
    \item Provides valuable insights for SLAM in high-speed autonomous vehicles in structured environments.
    \item Comparison methodology can be adapted for evaluating other SLAM approaches.
    \item Findings on computational efficiency are relevant for embedded systems.
    \item Challenges with dynamic environments highlight considerations for robust localisation.
    \item Sensor fusion approaches offer practical guidelines for hardware/integration.
    \item Builds on probabilistic SLAM foundations (Bayesian filtering, EKF, GraphSLAM as least squares, FastSLAM as particle filter with Rao-Blackwellisation).
    \item Discusses JCBB for data association and the Markov assumption.
    \item Situated in FSD competition (KA-RaceIng car), noting standardised cone tracks and FSD-specific SLAM requirements (real-time, robustness, high-speed, map/localise phases).
    \item References core SLAM literature, AMZ Racing publications, and sensor fusion techniques.
    \item Investigate current versions/advancements in GraphSLAM and EKF SLAM since 2021.
    \item Consider the trade-off between SLAM accuracy (e.g., GraphSLAM) and the computational budget available for both SLAM and the GA path planner on the target hardware.
\end{itemize}